---
title: "Plot Exit"
subtitle: "Make plots fall apart or turn into bats"
format: revealjs
revealjs-plugins:
  - plot-exit
---

## Gravity: left-to-right sweep

`.gravity-exit` makes the marks fall, sweeping from left to right. Press the forward key to try it.

::: {.fragment .gravity-exit}
<!-- Left-to-right sweep (no modifier classes). -->

```{r}
#| dev: svg

library(ggplot2)

ggplot(mpg, aes(displ, hwy, color = class)) +
  geom_point() +
  theme_minimal()
```
:::


## Gravity: random order

Adding `.random-order` makes the marks fall in a random order instead of sweeping.

::: {.fragment .gravity-exit .random-order}
<!-- Random fall order instead of the left-to-right sweep. -->

```{r}
#| dev: svg

library(ggplot2)

ggplot(mpg, aes(displ, hwy, color = class)) +
  geom_point() +
  theme_minimal()
```
:::

## Gravity: trails

Adding `.trails` leaves fading motion trails behind each falling mark.

::: {.fragment .gravity-exit .random-order .trails}
<!-- Adds fading motion trails behind each falling element. -->

```{r}
#| dev: svg

library(ggplot2)

ggplot(mpg, aes(displ, hwy, color = class)) +
  geom_point() +
  theme_minimal()
```
:::

## Gravity: only some marks

Setting `data-n="5"` makes only 5 randomly chosen marks fall; the rest stay put.

::: {.fragment .gravity-exit .random-order data-n="5"}
<!-- Only 5 randomly chosen elements fall; the rest stay put. -->

```{r}
#| dev: svg

library(ggplot2)

ggplot(mpg, aes(displ, hwy, color = class)) +
  geom_point() +
  theme_minimal()
```
:::

## Bats: October is near

`.bats-exit` morphs each mark into a bat that flutters off and fades out.

::: {.fragment .bats-exit .random-order}
<!-- Each mark morphs into a bat silhouette (bat.svg), then flutters off and fades out. -->

```{r}
#| dev: svg

library(ggplot2)

ggplot(mpg, aes(displ, hwy, color = class)) +
  geom_point() +
  theme_minimal() +
  theme(panel.grid = element_blank()) +
  scale_color_viridis_d(option = "C")
```
:::

## Bats: only some marks

`data-n="10"` works here too: only 10 randomly chosen marks turn into bats.

::: {.fragment .bats-exit .random-order data-n="10"}
<!-- Only 10 randomly chosen marks turn into bats; the rest stay put. -->

```{r}
#| dev: svg

library(ggplot2)

ggplot(mpg, aes(displ, hwy, color = class)) +
  geom_point() +
  theme_minimal() +
  theme(panel.grid = element_blank()) +
  scale_color_viridis_d(option = "C")
```
:::
